---
title: "DataScienceHW1"
format: html
editor: visual
editor_options: 
  chunk_output_type: inline
---

# Test

## What do you think being a data scientist is about?

I think it's all about analyzing data effectively and efficiently.

## 

## What differences/similarities do you see between data scientists and statisticians?

Some similarities that I see are the analytic tools used (such as RSS, chi squared, etc.) between data scientists and statisticians. I also think data scientists are more versatile as they will require skills that software developers need, as well as statisticians.

## 

## How do you view yourself in relation to these two areas?

I am neither a data scientist or a statistician, I am an engineer by profession. However, I would say I am close to a statistician than a data scientist, as programming typically is NOT my forte.

## 

## 

# R code below

```{r}
  y <- density(iris$Sepal.Length)
```

## The following R code below determines the class, type, and structure of the object "y".

### This chunk of code determines the class of the object.

```{r}
#| echo: FALSE
  class(y)
```

### This chunk of code determines the type of the object.

```{r}
#| echo: FALSE
  typeof(y)
```

### This chunk of code determines the internal structure of the object.

```{r}
#| echo: FALSE
  str(y)
```
